ResultsNPS

### 2019-10-25 R/nps_reports/results.Rmd
changes in R and python to get correct logs from fixLP matheuristic.

```{r}
t1_rel_filt <- t1_rel[t1_rel<20]
filtered_quant <- (1 - (t1_rel_filt %>% length) / (t1_rel %>% length))*100
```

@@

```{r}
filtered_q_perf <- quality_perf %>% filter(between(dif_perc, -10, 10))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%) have been taken out to help better visualize it.

>>>>

```{r}
# this takes 10% from right side
t1_rel_filt <- t1_rel[t1_rel<quantile(t1_rel, 0.90)]
filtered_quant <- (1 - (t1_rel_filt %>% length) / (t1_rel %>% length))*100
```

@@

```{r}

# this takes 5% from each side
filtered_q_perf <- quality_perf %>% filter(dif_perc %>% between(., quantile(., c(0.05)), quantile(., c(0.95))))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%) have been taken out to help better visualize it.
